%-------------------------
% Resume in Latex
% Author : Yingke Ding
% Template: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[T1]{fontenc}
\usepackage{tgtermes}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex,hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Yingke (Derrick) Ding}} & Email : \href{mailto:yingke.dev@gmail.com}{yingke.dev@gmail.com}\\
  \href{https://github.com/dykderrick}{\underline{https://github.com/dykderrick}} & Mobile : \href{tel:+12065919245}{+1-206-591-9245} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
  \resumeSubHeadingListStart
      \item Interned as SDE at \textbf{Amazon.com} devices team. Designed and implemented a \textbf{PostgreSQL} system to covert unstructured data, and built a web app using \textbf{Golang} RESTful APIs and \textbf{React.js} frontend.
      \item Proud to have developed innovative apps for Android (\textbf{Kotlin}), iOS / watchOS (\textbf{Swift}) through on-campus projects.
  \resumeSubHeadingListEnd
  
 %--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python 3, Go, Java, Swift, Kotlin, JavaScript (React.js)}
     %\hfill
   }
   \item{
     \textbf{Technologies}{: Git, Django, Docker, GraphQL, REST, Redis, Unix/Bash, PostgreSQL, MongoDB, AWS}
     %\hfill
   }
 \resumeSubHeadingListEnd




%-------------------------------------------



%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon}{Beijing, China}
      {Software Dev Engineer Intern}{Mar 2022 - Aug 2022}
      \resumeItemListStart
        \resumeItem{Data Normalization}
          {Converted over 300 MB of unstructured manufacturing and testing data on Amazon devices to normalized relational data. Stored the data into a well-designed \textbf{PostgreSQL} database system with \textbf{Python} scripts and \href{https://www.djangoproject.com/}{\textbf{\underline{Django}}} framework. The overall query time for a single entry has been reduced \textbf{30 percent} compared to the original.}
        \resumeItem{API Center}
          {Used \textbf{Golang} \href{https://github.com/gin-gonic/gin}{\textbf{\underline{Gin}}} framework to build a \textbf{RESTful} API service center to handle requests and serve specific data as response. Design principles followed Google Cloud API Design Guide. Adopted \href{https://github.com/jmoiron/sqlx}{\textbf{\underline{SQLX}}} as the ORM to the database.}
        \resumeItem{Web-based Application}
          {Used \textbf{React.js}, \textbf{Bootstrap} templating components and \textbf{Apache Echarts} data visualization tool to implement a Web Application. Deployed the app to an \textbf{AWS} EC2 instance via a dedicated \textbf{docker} compose config.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%
%--------Projects------------
\section{Featured Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MusicFit (\href{https://github.com/dykderrick/MusicFit}{\underline{GitHub}})}{Beijing, China}
      {Pervasive HCI Lab, Tsinghua University}{Apr 2022 - Jun 2022}
      \resumeItemListStart
        \item{
        With a Model-View-ViewModel design pattern (\textbf{SwiftUI}), this iOS app uses 
          \href{https://developer.apple.com/documentation/coremotion}{\textbf{\underline{Core Motion}}}
          framework to detect the user's physical behavioral changes (ranging from walking, running to resting).
          }
          
          \item{
          Integrated \href{https://developer.apple.com/documentation/applemusicapi/}{\textbf{\underline{Apple Music API}}} with \href{https://github.com/Alamofire/Alamofire}{\textbf{\underline{Alamofire}}} framework and implemented a song player that can automatically controls now-playing songs in different playlists based on user's workout motion.
          }
          
      \resumeItemListEnd
      
    \resumeSubheading
      {FitPal (\href{https://github.com/dykderrick/FitPal}{\underline{GitHub}})}{Beijing, China}
      {Pervasive HCI Lab, Tsinghua University}{Oct 2021 - Dec 2021}
      \resumeItemListStart
        \item{
        With a dedicated \textbf{Core ML model} trained through \href{https://developer.apple.com/machine-learning/create-ml/}{\textbf{\underline{Create ML}}}, this watchOS app can start a workout session, automatically record movement counts and store workout results into Apple Health app.
        }
        
        \item{
        Workout tracking functionality is built using Apple \href{https://developer.apple.com/documentation/healthkit}{\textbf{\underline{HealthKit}}} while Watch-faces are built with \textbf{Storyboard} MVC.
        }
          
      \resumeItemListEnd
      
    \resumeSubheading
      {Improve Restaurant Service Efficiency with NFC Chips}{Remote}
      {Undergrad Final Year Project}{Feb 2021 - May 2021}
      \resumeItemListStart
        \resumeItem{Android Restaurant Ordering App (\href{https://github.com/dykderrick/Restaurant-Ordering-NFC-Android}{\underline{GitHub}})}
          {Used \href{https://www.mongodb.com/docs/realm/sdk/kotlin/}{\textbf{\underline{Realm Kotlin SDK}}} to implement restaurant table registration, menu fetch, customer ordering and real-time progress viewing. Integrated \href{https://developer.paypal.com/docs/api/payments/v1/}{\textbf{\underline{PayPal Payments API}}} to simulate bill payment process.
          }
        \resumeItem{Web-based Administrative System (\href{https://github.com/dykderrick/Restaurant-Backend-Management-System-Django}{\underline{GitHub}})}
          {For restaurant chefs to view and manage orders. The webapp uses \textbf{MongoDB} hosted on \href{https://www.mongodb.com/atlas/database}{\textbf{\underline{Atlas}}} as database, and \textbf{Django} as framework.}
          
      \resumeItemListEnd
     
     
  \resumeSubHeadingListEnd
  
  
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Dual Degree II: Master of Science in Technology Innovation}{Sep. 2022 -- Mar. 2024 (Expected)}
    \resumeSubheading
      {Tsinghua University}{Beijing, China}
      {Dual Degree I: Master of Engineering (Major: \textbf{Computer Science})}{Aug. 2021 -- Mar. 2024 (Expected)}
    \resumeSubheading
      {Beijing University of Posts and Telecommunications}{Beijing, China}
      {Bachelor of Science \& Engineering (Major: \textbf{Internet of Things Eng.}); GPA: 3.72 / 4.00}{Sep. 2017 -- Jun. 2021}
  \resumeSubHeadingListEnd

%
\end{document}
